Columnar VCF using Zarr

### 2024-03-12 paper.tex
Remove code block

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=6cm]{figures/subset-matrix-compute} &
\begin{tcolorbox}[width=7cm]
\begin{minted}[fontsize=\footnotesize]{python}
# TODO not sure how best to illustrate this. Trying out various
# options

ds = sgkit.load_dataset(ds_path)
dss = ds.isel(
    variants=slice(...),
    samples=(slice(...)))
df = sgkit_afdist(dss)

# bcftools
bcftools view PATH -S ... -r...
| bcftools +fill-tags | bcftools +af-dist

# genozip
genocat PATH -r ... -s ...
| bcftools +fill-tags | bcftools +af-dist

# Complex query
df = pd.read_csv("sample_info.csv",
    sep="\t").set_index("sample_id")
dss = ds.isel(
    samples=df.decade[ds.sample_id.values] >= 1950)
sgkit_afdist(dss)

# Corresponding shell
% tail -n+2 sample_info.csv | awk '$2 >= 1950'
    | cut -f1 > samples.txt
bcftools view PATH -s samples.txt
    | bcftools +fill-tags | bcftools +af-dist
\end{minted}
\end{tcolorbox}
\end{tabular}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute.
(C) A simplified version of the source code used for these benchmarks.
\label{fig-subset-matrix-compute}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=6cm]{figures/subset-matrix-compute}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute.
(C) A simplified version of the source code used for these benchmarks.
\label{fig-subset-matrix-compute}}
\end{figure*}
